Report - Latest Rodent Data

### 2019-03-05 index.Rmd
tidying up the website markdowns

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
'%>%' <- magrittr::'%>%'
source("tools/forecast_tools.R")
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=6}
plot_cast_ts()
```

@@

```{r speciesforecasts, echo=FALSE}
plot_cast_point()
```

@@

These figures are similar to the primary Total Abundance Forecast above, but for the abundance of three common rodent species. 
```{r highabund_ts_forecasts, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
most_ab <- select_most_ab_spp()
for(i in 1:3){
  plot_cast_ts(species = most_ab[i])
}
```

>>>>

@@

```{r, total_forecast, echo=FALSE, fig.width=8, fig.height=6}
plot_cast_ts()
```

@@

```{r, species_forecasts, echo=FALSE}
plot_cast_point()
```

@@

These figures are similar to the primary Total Abundance Forecast above, but for the abundance of three common rodent species. 
```{r, highabund_ts_forecasts, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
most_ab <- select_most_ab_spp()
for(i in 1:3){
  plot_cast_ts(species = most_ab[i])
}
```

### 2019-03-05 report.Rmd
tidying up the website markdowns

Here's the most recent forecast for which observations have been made. The actual data (blue) are plotted in comparison to the forecast performed right before data collection (white, with error bars) for the control (unmanipulated) plots (top) and all plots together (bottom):
```{r, echo=FALSE}
plot_cast_point(with_census = TRUE)
```

```{r, echo=FALSE}
plot_cast_point(with_census = TRUE, level = "All")
```

>>>>

Here's the most recent forecast for which observations have been made. The actual data (blue) are plotted in comparison to the forecast performed right before data collection (white, with error bars) for the control (unmanipulated) plots (top) and all plots together (bottom):
```{r, with_census_controls, echo=FALSE}
plot_cast_point(with_census = TRUE)
```

```{r, with_census_all, echo=FALSE}
plot_cast_point(with_census = TRUE, level = "All")
```
